Typing a linear \picalc

### 2020-02-10 paper/paper.tex
Change to LIPIcs

\documentclass{scrartcl}

\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{todonotes}
\usepackage{enumitem}
\setlist{parsep=0pt,listparindent=\parindent}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[many]{tcolorbox}

% Links and their colors
\usepackage[
  colorlinks=true,
  linkcolor=darkgray,
  citecolor=darkgray,
  urlcolor=darkgray,
  ]{hyperref}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Typechecking a linear \picalc}
\author{Uma Zalakain}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Definition
Let $\Gamma \types P \boxtimes \Delta$ and $\Gamma - Delta \equiv \Xi - \phi$.
Then $\Xi \types P \boxtimes \phi$.

By defining of $\uplus$ as a total function, $\Gamma - \Delta$ is no longer
functional: $\omega - \omega$ results in any multiplicity, including $0$. Therefore
$\Xi \types P \boxtimes \phi$ would imply that such a variable cannot appear in $P$.

@@

\footnotesize
\bibliographystyle{alpha}
\bibliography{paper}
\end{document}

>>>>

\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate,authorcolumns]{lipics-v2019}

\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{todonotes}
\usepackage{enumitem}
\setlist{parsep=0pt,listparindent=\parindent}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[many]{tcolorbox}
\bibliographystyle{plainurl}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Typing a linear \picalc}
\author{Uma Zalakain}{University of Glasgow, Scotland}
       {uma.zalakain.1@research.gla.ac.uk}{https://orcid.org/0000-0002-3268-9338}{}
\author{Ornela Dardha}{University of Glasgow, Scotland}
       {ornela.dardha@glasgow.ac.uk}{https://orcid.org/0000-0001-9927-7875}{}
\authorrunning{U. Zalakain and O. Dardha}
\Copyright{Uma Zalakain and Ornela Dardha}
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003752.10003753.10003761.10003764</concept_id>
<concept_desc>Theory of computation~Process calculi</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[300]{Theory of computation~Process calculi}
\keywords{pi calculus, linear, types, concurrency}
\supplement{\url{https://github/umazalakain/typing-linear-pi}}
\acknowledgements{I want to thank \dots}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\maketitle

@@

Definition
Let $\Gamma \type P \boxtimes \Delta$ and $\Gamma - Delta \equiv \Xi - \phi$.
Then $\Xi \type P \boxtimes \phi$.

By defining of $\uplus$ as a total function, $\Gamma - \Delta$ is no longer
functional: $\omega - \omega$ results in any multiplicity, including $0$. Therefore
$\Xi \type P \boxtimes \phi$ would imply that such a variable cannot appear in $P$.

@@

\bibliography{paper}
\end{document}
